Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2015-12-29 reviews/response-jarosch.tex

Actual parameter values for $A_c$, $A_w$, $Q_c$, $Q_w$ and $E_{SIA}$ used in
our simulations are given in Table~\ref{tab:rheo_params}, while the effect of
the three different parametrisations on temperature-dependent ice softness,
$A$, is illustrated in Fig.~\ref{fig:sens_plot_rheo}.

\begin{table*}
  \caption{Rheologic parameter values used in the sensitivity test.}
  \label{tab:rheo_params}
  \centering
  {\begin{tabular}{l|ccccc}
    \tophline
    Config. & $A_c$ & $A_w$ & $Q_c$ & $Q_w$ & $E_{SIA}$ \\
            & \multicolumn{2}{c}{(\unit{Pa^{-3}\,s^{-1}})}
            & \multicolumn{2}{c}{(\unit{J\,mol^{-1}})} & \\
    \middlehline
    Default$^1$  & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 \\
    Hard ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 1 \\
    Soft ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 5 \\
    \bottomhline
  \end{tabular}}
  \belowtable{According to $^1$\citet{Paterson.Budd.1982} and
              $^2$\citet{Cuffey.Paterson.2010}.}
\end{table*}

\begin{figure}
    \centering
    \includegraphics{sens_plot_rheo}
    \caption{Ice softness parameter, $A$, as a function of pressure-adjusted
             temperature, $T_{pa}$, for the default \citet{Paterson.Budd.1982},
             hard ice \citet{Cuffey.Paterson.2010}, and soft ice
             \citet[with $E_{SIA}=5$]{Cuffey.Paterson.2010} rheologies, using
             a linear scale (top panel) and logarithmic scale (bottom panel).}
    \label{fig:sens_plot_rheo}
\end{figure}

\clearpage  % moving on to basal sliding

In our simulations, basal sliding is governed by a~pseudo-plastic sliding law,
already given in the manuscript but recalled here for the sake of completeness,
%
\begin{equation}
    \label{eqn:pseudoplastic}
    \vec{\tau}_b = -\tau_c \frac{\vec{v}_b}{{v_{th}}^q\,|\vec{v}_b|^{1-q}} \,,
\end{equation}
%
which relates the bed-parallel shear stresses, $\vec{\tau}_b$, to the sliding
velocity, $\vec{v}_b$. The yield stress, $\tau_c$, is modelled using the
Mohr--Coulomb criterion,
%
\begin{equation}
   \tau_c = c_0 + N\,\tan{\phi} \,,
\end{equation}
%
where cohesion, $c_0$, is assumed to be zero. Effective pressure, $N$,
is related to the ice overburden stress, $\rho gh$, and the modelled amount of
subglacial water, using a formula derived from laboratory experiments with till
extracted from the base of Ice Stream B in West Antarctica
\citep[Eqn.~23]{Tulaczyk.etal.2000, Bueler.Pelt.2015},
\begin{equation}
    N = \delta \rho gh \, 10^{(e_0/C_c) (1 - (W/W_{max}))} \,,
\end{equation}
where $\delta$ sets the minimum ratio between the effective pressure, $N$, and
the ice overburden stress, $\rho gh$, $e_0$ is a measured reference void ratio
and $C_c$ is a measured compressibility coefficient. The amount of water at the
base, $W$, varies from zero to $W_{max}$, a threshold above which additional
melt water is assumed to drain off instantaneously.

In our sensitivity test, we set constant the pseudo-plastic sliding exponent,
$q=0.25$, and the threshold velocity, $v_{th}=100$\,\unit{m\,s^{-1}}, according
to values used by \citet{Aschwanden.etal.2013}, the till cohesion, $c_0=0$,
whose measured values are consistently negligible
\citep[p.~268]{Tulaczyk.etal.2000, Cuffey.Paterson.2010}, the till reference
void ratio, $e_0=0.69$, and the till compressibility coefficient, $C_c=0.12$,
according to the only measurements available to our knowledge by
\citep{Tulaczyk.etal.2000}.

We also use a constant spatial distribution of the till friction angle, $\phi$,
whose values vary from 15 to 45{\degree} as a piecewise-linear function of
modern bed elevation, with the lowest value occuring below modern sea level
(0\,m above sea level, m~a.s.l.) and the highest value occuring above the
generalised elevation of the highest shorelines
\citep[200\,m~a.s.l.,][Fig.~5]{Clague.1981}. This range of value span over the
range of measured values for glacial till of 18 to 40{\degree}
\citep[p.~268]{Cuffey.Paterson.2010}. It accounts for frictional basal
conditions associated with discontinuous till cover at high elevations, and
a~weakening of till associated with the presence of marine sediments at low
elevations (cf. \citealp{Martin.etal.2011};
\citealp[supplement]{Aschwanden.etal.2013}; \citealp{PISM-authors.2015}).

An additional simulation with a constant till friction angle, $\phi=30\degree$,
corresponding to the average value in \citet[p.~268]{Cuffey.Paterson.2010}, was
actually performed, but the induced variability was small as compared to that
which will be presented here, and therefore we decided to not include this run.

On the other hand, we test different values for the minimum ratio between the
effective pressure and the overburden stress, $\delta$, and the maximum water
height in the till, $W_{max}$, as follow.

\begin{itemize}
    \item{Our \emph{default} configuration used in the control run and all other
          simulations in the manuscript include $\delta=0.02$ and
          $W_{max}=2$\,m as in \citet{Bueler.Pelt.2015}.}
    \item{Our \emph{hard bed} configuration use $\delta=0.01$ and
          $W_{max}=1$\,m.}
    \item{Our \emph{soft bed} configuration use $\delta=0.05$ and
          $W_{max}=5$\,m.}
\end{itemize}

### 2015-12-29 reviews/response-jarosch.tex

We also use a constant spatial distribution of the till friction angle, $\phi$,
whose values vary from 15 to 45{\degree} as a piecewise-linear function of
modern bed elevation, with the lowest value occuring below modern sea level
(0\,m above sea level, m~a.s.l.) and the highest value occuring above the
generalised elevation of the highest shorelines
\citep[200\,m~a.s.l.,][Fig.~5]{Clague.1981}. This range of value span over the
range of measured values for glacial till of 18 to 40{\degree}
\citep[p.~268]{Cuffey.Paterson.2010}. It accounts for frictional basal
conditions associated with discontinuous till cover at high elevations, and
a~weakening of till associated with the presence of marine sediments at low
elevations (cf. \citealp{Martin.etal.2011};
\citealp[supplement]{Aschwanden.etal.2013}; \citealp{PISM-authors.2015}).

An additional simulation with a constant till friction angle, $\phi=30\degree$,
corresponding to the average value in \citet[p.~268]{Cuffey.Paterson.2010}, was
actually performed, but the induced variability was small as compared to that
which will be presented here, and therefore we decided to not include this run.

On the other hand, we test different values for the minimum ratio between the
effective pressure and the overburden stress, $\delta$, and the maximum water
height in the till, $W_{max}$, as follow.

\begin{itemize}
    \item{Our \emph{default} configuration used in the control run and all other
          simulations in the manuscript include $\delta=0.02$ and
          $W_{max}=2$\,m as in \citet{Bueler.Pelt.2015}.}
    \item{Our \emph{hard bed} configuration use $\delta=0.05$ and
          $W_{max}=5$\,m.}
    \item{Our \emph{soft bed} configuration use $\delta=0.01$ and
          $W_{max}=1$\,m.}
\end{itemize}

These parameter choices are recalled in Table~\ref{tab:ntil_params}, while the
effect of the three different parametrisations on the effective pressure on
the till, $N$, in response to water content, $W$, is illustrated in
Fig.~\ref{fig:sens_plot_ntil}.

\begin{figure}
    \centering
    \includegraphics{sens_plot_ntil}
    \caption{Effective pressure, $N$, as a function of water height at the
             base, $W$, for the default ($\delta=0.02$, $W_{max}=2$\,m),
             hard bed ($\delta=0.05$, $W_{max}=5$\,m), and soft bed
             ($\delta=0.01$, $W_{max}=1$\,m) sliding parametrisations, using a
             linear scale (top panel) and a logarithmic scale (bottom panel).}
    \label{fig:sens_plot_ntil}
\end{figure}

### 2015-12-29 reviews/response-jarosch.tex

An additional simulation with a constant till friction angle, $\phi=30\degree$,
corresponding to the average value in \citet[p.~268]{Cuffey.Paterson.2010}, was
actually performed, but the induced variability was small as compared to that
which will be presented here, and therefore we decided to not include this run.

On the other hand, we test different values for the minimum ratio between the
effective pressure and the overburden stress, $\delta$, and the maximum water
height in the till, $W_{max}$, as follow.

\begin{itemize}
    \item{Our \emph{default} configuration used in the control run and all other
          simulations in the manuscript include $\delta=0.02$ and
          $W_{max}=2$\,m as in \citet{Bueler.Pelt.2015}.}
    \item{Our \emph{hard bed} configuration use $\delta=0.05$ and
          $W_{max}=5$\,m.}
    \item{Our \emph{soft bed} configuration use $\delta=0.01$ and
          $W_{max}=1$\,m.}
\end{itemize}

These parameter choices are recalled in Table~\ref{tab:slip_params}, while the
effect of the three different parametrisations on the effective pressure on
the till, $N$, in response to water content, $W$, is illustrated in
Fig.~\ref{fig:sens_plot_ntil}.

\begin{table*}
  \caption{Basal sliding parameter values used in the sensitivity test.}
  \label{tab:slip_params}
  \centering
  {\begin{tabular}{l|cc}
    \tophline
    Config. & $\delta$ & $W_{max}$ \\
            &          & m \\
    \middlehline
    Default$^1$ & 0.02 & 2 \\
    Hard bed    & 0.05 & 5 \\
    Soft bed    & 0.01 & 1 \\
    \bottomhline
  \end{tabular}}
  \belowtable{$^1$According to \citet{Bueler.Pelt.2015}.}
\end{table*}

### 2015-12-30 reviews/response-jarosch.tex

On the other hand, we test different values for the two creep parameters, $A_c$
and $A_w$, the two activation energies, $Q_c$ and $Q_w$, and the SIA
enhancement factor, $E_{SIA}$, as follow.

\begin{itemize}
    \item{Our \emph{default} configuration used in the control run and all other
          simulations in the manuscript include rheologic parameters, $A_c$,
          $A_w$, $Q_c$ and $Q_w$, derived from \citet{Paterson.Budd.1982} and
          given in \citet[Eqn.~5]{Bueler.Brown.2009}, and $E_{SIA}=1$.}
    \item{Our \emph{hard ice} configuration include rheologic parameters,
          $A_c$, $A_w$, $Q_c$ and $Q_w$, derived from
          \citet[p.~72 and 76]{Cuffey.Paterson.2010}, and $E_{SIA}=1$, which
          correspond to a stiffer rheology than that used in the control run.}
    \item{Our \emph{soft ice} configuration include rheologic parameters,
          $A_c$, $A_w$, $Q_c$ and $Q_w$, derived from
          \citet[p.~72 and 76]{Cuffey.Paterson.2010}, and $E_{SIA}=5$, the
          recommended value for ice age polar ice
          \citep[p.~77]{Cuffey.Paterson.2010}.}
\end{itemize}

An additional simulation with rheologic parameters, $A_c$, $A_w$, $Q_c$ and
$Q_w$, derived from \citet{Cuffey.Paterson.2010}, and $E_{SIA}=2$, the
recommended value for Holocene polar ice \citep[p.~77]{Cuffey.Paterson.2010}
was performed, but its results were very similar to that of our default run,
thus we decided to not present it here.

Actual parameter values for $A_c$, $A_w$, $Q_c$, $Q_w$ and $E_{SIA}$ used in
our simulations are given in Table~\ref{tab:sens_params}, while the effect of
the three different parametrisations on temperature-dependent ice softness,
$A$, is illustrated in Fig.~\ref{fig:sens_plot_rheo}.

\begin{table*}
  \caption{Parameter values used in the sensitivity test.}
  \label{tab:sens_params}
  \centering\makebox[\textwidth]
  {\begin{tabular}{l|ccccc|cc}
    \tophline
    Config. & $A_c$ & $A_w$ & $Q_c$ & $Q_w$ & $E_{SIA}$
            & $\delta$ & $W_{max}$ \\
            & \multicolumn{2}{c}{(\unit{Pa^{-3}\,s^{-1}})}
            & \multicolumn{2}{c}{(\unit{J\,mol^{-1}})}
            & & & (m) \\
    \middlehline
    Default$^1$  & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.02 & 2 \\
    \middlehline
    Hard ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 1 & 0.02 & 2 \\
    Soft ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 5 & 0.02 & 2 \\
    \middlehline
    Hard bed     & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.05 & 5 \\
    Soft bed     & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.01 & 1 \\
    \bottomhline
  \end{tabular}}
  \belowtable{After $^1$\citet{Paterson.Budd.1982,Bueler.Pelt.2015};
              and $^2$\citet{Cuffey.Paterson.2010}.}
\end{table*}

@@

An additional simulation with a constant till friction angle, $\phi=30\degree$,
corresponding to the average value in \citet[p.~268]{Cuffey.Paterson.2010}, was
actually performed, but the induced variability was small as compared to that
which will be presented here, and therefore we decided to not include this run.

On the other hand, we test different values for the minimum ratio between the
effective pressure and the overburden stress, $\delta$, and the maximum water
height in the till, $W_{max}$, as follow.

\begin{itemize}
    \item{Our \emph{default} configuration used in the control run and all other
          simulations in the manuscript include $\delta=0.02$ and
          $W_{max}=2$\,m as in \citet{Bueler.Pelt.2015}.}
    \item{Our \emph{hard bed} configuration use $\delta=0.05$ and
          $W_{max}=5$\,m.}
    \item{Our \emph{soft bed} configuration use $\delta=0.01$ and
          $W_{max}=1$\,m.}
\end{itemize}

The effect of the three different parametrisations on the effective pressure on
the till, $N$, in response to water content, $W$, is illustrated in
Fig.~\ref{fig:sens_plot_ntil}.
All parameter choices are recalled in Table~\ref{tab:sens_params}.

### 2015-12-30 reviews/response-jarosch.tex

\begin{itemize}
    \item{Our \emph{default} configuration used in the control run and all other
          simulations in the manuscript include rheologic parameters, $A_c$,
          $A_w$, $Q_c$ and $Q_w$, derived from \citet{Paterson.Budd.1982} and
          given in \citet[Eqn.~5]{Bueler.Brown.2009}, and $E_{SIA}=1$.}
    \item{Our \emph{hard ice} configuration include rheologic parameters,
          $A_c$, $A_w$, $Q_c$ and $Q_w$, derived from
          \citet[p.~72 and 76]{Cuffey.Paterson.2010}, and $E_{SIA}=1$, which
          correspond to a stiffer rheology than that used in the control run.}
    \item{Our \emph{soft ice} configuration include rheologic parameters,
          $A_c$, $A_w$, $Q_c$ and $Q_w$, derived from
          \citet[p.~72 and 76]{Cuffey.Paterson.2010}, and $E_{SIA}=5$, the
          recommended value for ice age polar ice
          \citep[p.~77]{Cuffey.Paterson.2010}.}
\end{itemize}

An additional simulation with rheologic parameters, $A_c$, $A_w$, $Q_c$ and
$Q_w$, derived from \citet{Cuffey.Paterson.2010}, and $E_{SIA}=2$, the
recommended value for Holocene polar ice \citep[p.~77]{Cuffey.Paterson.2010}
was performed, but its results were very similar to that of our default run,
thus we decided to not present it here.

Actual parameter values for $A_c$, $A_w$, $Q_c$, $Q_w$ and $E_{SIA}$ used in
our simulations are given in Table~\ref{tab:sens_params}, while the effect of
the three different parametrisations on temperature-dependent ice softness,
$A$, is illustrated in Fig.~\ref{fig:sens_plot_rheo}.

\begin{table*}
  \caption{Parameter values used in the sensitivity test.}
  \label{tab:sens_params}
  \centering\makebox[\textwidth]
  {\begin{tabular}{l|ccccc|cc|cc}
    \tophline
            & \multicolumn{5}{c|}{Rheology}
            & \multicolumn{2}{c|}{Sliding}
            & \multicolumn{2}{c}{GRIP scaling} \\
    Config. & $A_c$ & $A_w$ & $Q_c$ & $Q_w$ & $E_{SIA}$
            & $\delta$ & $W_{max}$ & $f$ & $T_{[32, 22]}$ \\
            & \multicolumn{2}{c}{(\unit{Pa^{-3}\,s^{-1}})}
            & \multicolumn{2}{c}{(\unit{J\,mol^{-1}})}
            & & & (m) \\
    \middlehline
    Default$^1$  & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.02 & 2 & 0.38 & 6.2 \\
    \middlehline
    Hard ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 1 & 0.02 & 2 & 0.37 & 6.0 \\
    Soft ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 5 & 0.02 & 2 & 0.40 & 6.6 \\
    \middlehline
    Hard bed     & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.05 & 5 & 0.36 & 5.9 \\
    Soft bed     & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.01 & 1 & 0.40 & 6.5 \\
    \bottomhline
  \end{tabular}}
  \belowtable{After $^1$\citet{Paterson.Budd.1982,Bueler.Pelt.2015};
              and $^2$\citet{Cuffey.Paterson.2010}.}
\end{table*}

@@

On the other hand, we test different values for the minimum ratio between the
effective pressure and the overburden stress, $\delta$, and the maximum water
height in the till, $W_{max}$, as follow.

\begin{itemize}
    \item{Our \emph{default} configuration used in the control run and all other
          simulations in the manuscript include $\delta=0.02$ and
          $W_{max}=2$\,m as in \citet{Bueler.Pelt.2015}.}
    \item{Our \emph{hard bed} configuration use $\delta=0.05$ and
          $W_{max}=5$\,m.}
    \item{Our \emph{soft bed} configuration use $\delta=0.01$ and
          $W_{max}=1$\,m.}
\end{itemize}

The effect of the three different parametrisations on the effective pressure on
the till, $N$, in response to water content, $W$, is illustrated in
Fig.~\ref{fig:sens_plot_ntil}.
All parameter choices are recalled in Table~\ref{tab:sens_params}.

Finally, we adjusted the GRIP linear scaling factor for each run, so that they
result in a similar glaciated area at the Last Glacial Maximum (LGM) to that
modelled with the default configuration (Table~\ref{tab:sens_params}).

@@

\begin{figure}
    \centering
    \includegraphics{sens_plot_ntil}
    \caption{Effective pressure, $N$, as a function of water height at the
             base, $W$, for the default ($\delta=0.02$, $W_{max}=2$\,m),
             hard bed ($\delta=0.05$, $W_{max}=5$\,m), and soft bed
             ($\delta=0.01$, $W_{max}=1$\,m) sliding parametrisations, using a
             linear scale (top panel) and a logarithmic scale (bottom panel).}
    \label{fig:sens_plot_ntil}
\end{figure}

\clearpage  % moving on to the results

\begin{figure*}
  \includegraphics{sens_ts}
  \caption{Modelled sea-level relevant ice volume through the last 120\,ka
           in the simulation forced by the GRIP paleo-climate record, using
           default parameters (black curves), different ice rheology parameters,
           (top panel) and different basal sliding parameters (bottom panel).
           Gray fields indicate Marine Oxygen Isotope Stage (MIS) boundaries
           for MIS~2 and MIS~4 according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{Lisiecki.Raymo.2005}.}
  \label{fig:sens_ts}
\end{figure*}

### 2015-12-30 reviews/response-jarosch.tex

\begin{figure}
    \centering
    \includegraphics{sens_plot_ntil}
    \caption{Effective pressure, $N$, as a function of water height at the
             base, $W$, for the default ($\delta=0.02$, $W_{max}=2$\,m),
             hard bed ($\delta=0.05$, $W_{max}=5$\,m), and soft bed
             ($\delta=0.01$, $W_{max}=1$\,m) sliding parametrisations, using a
             linear scale (top panel) and a logarithmic scale (bottom panel).}
    \label{fig:sens_plot_ntil}
\end{figure}

\clearpage  % moving on to the results

\begin{figure*}
  \includegraphics{sens_ts}
  \caption{Modelled sea-level relevant ice volume through the last 120\,ka
           in the simulation forced by the GRIP paleo-climate record, using
           default parameters (black curves), different ice rheology parameters,
           (top panel) and different basal sliding parameters (bottom panel).
           Gray fields indicate Marine Oxygen Isotope Stage (MIS) boundaries
           for MIS~2 and MIS~4 according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{Lisiecki.Raymo.2005}.}
  \label{fig:sens_ts}
\end{figure*}

\begin{table*}
  \caption{Extremes in Cordilleran ice sheet volume and extent corresponding to
           MIS~4, 3 and 2 using the GRIP paleo-climate forcing with each
           parameter configuration (Fig.~\ref{fig:sens_ts}). Relative
           differences (r. diff.) give rough error estimates related to
           varying selected ice rheology and basal sliding parameters
           (Table.~\ref{tab:sens_params}).}
  \label{tab:sens_extrema}
  \centering\makebox[\textwidth]
  {\begin{tabular}{l*{3}{|ccc}}
    \tophline
             & \multicolumn{3}{c}{Age (ka)}
             & \multicolumn{3}{c}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m~s.l.e.)} \\
    Config.  &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    Default  &  57.59 &  42.91 &  19.14
             &   1.93 &   0.67 &   2.09
             &   7.43 &   1.54 &   8.62 \\
    \middlehline
    Hard ice &  57.32 &  42.90 &  19.14
             &   1.90 &   0.75 &   2.12
             &   7.83 &   1.91 &   9.46 \\
    Soft ice &  58.89 &  49.97 &  21.57
             &   1.96 &   0.54 &   2.08
             &   6.58 &   1.03 &   6.88 \\
    R. diff. &    3\% &   16\% &   13\%
             &    3\% &   31\% &    2\%
             &   17\% &   57\% &   30\% \\
    \middlehline
    Hard bed &  57.31 &  42.91 &  19.14
             &   1.93 &   0.96 &   2.13
             &   7.99 &   2.89 &   9.31 \\
    Soft bed &  58.90 &  49.21 &  19.53
             &   1.88 &   0.55 &   2.05
             &   6.46 &   1.03 &   7.52 \\
    R. diff. &    3\% &   15\% &    2\%
             &    3\% &   62\% &    4\%
             &   21\% &  120\% &   21\% \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

\clearpage  % eventually moving on to the next point
